### 2020-07-16 article.tex
Several fixes, including URL

This continuous equation is discretized with $\mathbb{P}_3$ finite elements using FreeFEM. The script is available at \url{https://github.com/prj-/jolivet2020sisc}. Following timings and convergence histories have been obtained on $2{,}304$ processes of Ir\`ene, for solving a problem of dimension \pgfmathprintnumber{74618461}. By default, SLEPc applies at most 5 iterations of GMRES on each column of a so-called set of active columns. Since the option \pk{-eps\_lobpcg\_blocksize 40} is used for computing 20 eigenpairs, the size of the set varies between 40 to 1. This size corresponds to the number of right-hand sides in systems that will be solved throughout LOBPCG iterations. Instead of using \pk{KSPGMRES}, which does not handle blocking, \pk{KSPHPDDM} is used, with the pseudo-block GMRES. That means that, assuming the size of the set of active columns is 40, one LOBPCG iterations implies doing at most 5 GMRES iterations with 40 vectors simultaneously, using \pk{MatProductNumeric} and \pk{PCMatApply}, instead of doing at most $40\times 5$ successive GMRES iterations, using \pk{MatMult} and \pk{PCApply}. Results are gathered in~\cref{fig:lobpcg}. In the first line, the numbers of outer LOBPCG iterations are reported with the three different inner preconditioners mentioned above. \pk{PCASM} is known to yield a preconditioned operator whose condition number grows as the number of subdomains, here processes, increases. Thus, the number of outer iterations is higher than with \pk{PCHPDDM} or \pk{PCGAMG} since the inner solves are not converging to meaningful solutions in just 5 iterations. For both multilevel preconditioners, however, it seems that they perform an equivalent job since the difference in number of outer iterations is only 1. The second and third lines represent the number of times \pk{PCApply} and \pk{PCMatApply} are called. Since \pk{PCGAMG} does not handle blocking, at each pseudo-block GMRES iteration, \pk{PCApply} is called on all active columns. \pk{PCASM} and \pk{PCHPDDM} handle blocking, so only rely on \pk{PCMatApply}. In the fourth line, the time spent setting up the preconditioners is given. \pk{PCASM} is extremely cheap but not very robust numerically, while both multilevel preconditioners have a similar setup time. Eventually, in the last line, the time spent in the full eigensolve is given. Clearly, having both a \pk{KSP} and a \pk{PC} which can deal with multiple vectors efficiently is mandatory to achieve reasonable performance with such an outer solver that heavily relies on blocking.

@@

    \subsubsection{Coarse corrections customization}
Some other parameters may be adjusted to define how the one-level preconditioner
and the coarse grid operator interact. Besides the additive
correction shown in~\cref{eq:two}, end-users may select more numerically efficient
corrections~\cite{tang2009comparison,bastian1998additive} as:
\begin{align*}
    M'^{-1}_{\text{deflated}} &= Q + M^{-1}\left(I - AQ\right)\quad
    \text{(default)}\\
    M'^{-1}_{\text{balanced}} &= Q + \left(I - AQ\right)M^{-1}\left(I - AQ\right),
\end{align*}
with $Q = P \left(P^T A P\right)^{-1} P^T$. This is parameterized using the
options \pk{-pc\_hpddm\_coarse\_correction}
\pk{(deflated$|$additive$|$balanced)} or the routine
\pk{PCHPDDMSetCoarseCorrectionType}. It is important to keep in mind that all
these correction formulae may be applied to either a single vector or a block
of multiple vectors optimally. Indeed, the one-level preconditioner $M^{-1}$ is
applied with either \pk{PCApply} or \pk{PCMatApply}, and the
restriction-correction-interpolation operator $Q$ is applied in a block fashion
in HPDDM, and not column by column. See the effect of this strategy~\cref{sec:lobpcg}.

@@

The Cauchy stress tensor $\sigma$ is given by Hooke’s law: it can be expressed in terms of Young’s modulus $E$ and Poisson’s ratio $\nu$.

@@

In this third configuration, $M$ is the number of subdomains used to define the second-level domain decomposition, which is an aggregation of first-level subdomain.

@@

options is given in~\cref{fig:bratu-options}. Results can be reproduced using the FreeFEM script at \url{https://github.com/prj-/jolivet2020sisc}

@@

    \subfloat[\parbox{5cm}{\pk{SNES}, \pk{KSP}, and \pk{PC} options for the

@@

level using $10$ local eigenvectors per subdomains. The coarsest level is

@@

The magnitude of the electric field is plotted~\cref{fig:E}. For the
convergence history of the solver, it is~\cref{fig:BDDC}. The outer solver
reaches the prescribed convergence criterion in 17 iterations~\ref{pgfplots:res}. The number of

>>>>

This continuous equation is discretized with $\mathbb{P}_3$ finite elements using FreeFEM. The script is available at \url{https://github.com/prj-/jolivet2020petsc}. The following timings and convergence histories have been obtained on $2{,}304$ processes of Ir\`ene, for solving a problem of dimension \pgfmathprintnumber{74618461}. By default, SLEPc applies at most 5 iterations of GMRES on each column of a so-called set of active columns. Since the option \pk{-eps\_lobpcg\_blocksize 40} is used for computing 20 eigenpairs, the size of the set varies between 40 to 1. This size corresponds to the number of right-hand sides in systems that will be solved throughout LOBPCG iterations. Instead of using \pk{KSPGMRES}, which does not handle blocking, \pk{KSPHPDDM} is used, with the pseudo-block GMRES. That means that, assuming the size of the set of active columns is 40, one LOBPCG iterations implies doing at most 5 GMRES iterations with 40 vectors simultaneously, using \pk{MatProductNumeric} and \pk{PCMatApply}, instead of doing at most $40\times 5$ successive GMRES iterations, using \pk{MatMult} and \pk{PCApply}. Results are gathered in~\cref{fig:lobpcg}. In the first line, the numbers of outer LOBPCG iterations are reported with the three different inner preconditioners mentioned above. \pk{PCASM} is known to yield a preconditioned operator whose condition number grows as the number of subdomains, here processes, increases. Thus, the number of outer iterations is higher than with \pk{PCHPDDM} or \pk{PCGAMG} since the inner solves are not converging to meaningful solutions in just 5 iterations. For both multilevel preconditioners, however, it seems that they perform an equivalent job since the difference in number of outer iterations is only 1. The second and third lines represent the number of times \pk{PCApply} and \pk{PCMatApply} are called. Since \pk{PCGAMG} does not handle blocking, at each pseudo-block GMRES iteration, \pk{PCApply} is called on all active columns. \pk{PCASM} and \pk{PCHPDDM} handle blocking, so only rely on \pk{PCMatApply}. In the fourth line, the time spent setting up the preconditioners is given. \pk{PCASM} is extremely cheap but not very robust numerically, while both multilevel preconditioners have a similar setup time. Eventually, in the last line, the time spent in the full eigensolve is given. Clearly, having both a \pk{KSP} and a \pk{PC} which can deal with multiple vectors efficiently is mandatory to achieve reasonable performance with such an outer solver that heavily relies on blocking.

@@

    \subsubsection{Coarse corrections customization}
Some other parameters may be adjusted to define how the one-level preconditioner
and the coarse grid operator interact. Besides the additive
correction shown in~\cref{eq:two}, end-users may select more numerically efficient
corrections~\cite{tang2009comparison,bastian1998additive} as:
\begin{align*}
    M'^{-1}_{\text{deflated}} &= Q + M^{-1}\left(I - AQ\right)\quad
    \text{(default)}\\
    M'^{-1}_{\text{balanced}} &= Q + \left(I - AQ\right)M^{-1}\left(I - AQ\right),
\end{align*}
with $Q = P \left(P^T A P\right)^{-1} P^T$. This is parameterized using the
options \pk{-pc\_hpddm\_coarse\_correction}
\pk{(deflated$|$additive$|$balanced)} or the routine
\pk{PCHPDDMSetCoarseCorrectionType}. It is important to keep in mind that all
these correction formulae may be applied to either a single vector or a block
of multiple vectors optimally. Indeed, the one-level preconditioner $M^{-1}$ is
applied with either \pk{PCApply} or \pk{PCMatApply}, and the
restriction-correction-interpolation operator $Q$ is applied in a block fashion
in HPDDM, and not column by column. See the effect of this strategy in~\cref{sec:lobpcg}.

@@

The Cauchy stress tensor $\sigma$ is given by Hooke’s law: it can be expressed in terms of Young’s modulus $E$ and Poisson’s ratio $\nu$,

@@

In this third configuration, $M$ is the number of subdomains used to define the second-level domain decomposition, which is an aggregation of first-level subdomains.

@@

options is given in~\cref{fig:bratu-options}. Results can be reproduced using the FreeFEM script at \url{https://github.com/prj-/jolivet2020petsc}

@@

    \subfloat[\parbox{5cm}{\pk{SNES}, \pk{KSP}, and \pk{PC} options for

@@

level using $10$ local eigenvectors per subdomain. The coarsest level is

@@

The magnitude of the electric field is plotted in~\cref{fig:E}. The
convergence history of the solver is shown in~\cref{fig:BDDC}. The outer solver
reaches the prescribed convergence tolerance in 17 iterations~\ref{pgfplots:res}. The number of
